OG_cleaning

### 2019-07-29 OG-Analysis.Rmd
added in a IFNg subset

```{r read in data files}
setwd("/Applications/Old Computer/Day Lab/Flow-Data/clean")
CD4<-dplyr::select(read.csv("OG_CD4_bulk_summary_clean.csv"), -X, -X.1)
CD4_OG<-dplyr::select(read.csv("OG_CD4_OG_summary_clean.csv"), -X, -X.1)
CD4_OG_TH1<-dplyr::select(read.csv("OG_CD4_OG.TH1_summary_clean.csv"), -X, -X.1)
CD4_OG_GT<-dplyr::select(read.csv("OG_CD4_OG.TH1_summary_clean.csv"), -X, -X.1)
CD4_OG_TNF<-dplyr::select(read.csv("OG_CD4_OG.TNFa_summary_clean.csv"), -X, -X.1)
PBMC<-dplyr::select(read.csv("DonorInfo_clean.csv"), -X)
    PBMC<-PBMC[grep("OG", PBMC$used),]
mimosa<-dplyr::select(read.csv("OG_MIMOSA_clean.csv"), -X)
    mimosa<-dplyr::filter(mimosa, celltype=="CD4" & Exprate==0.01)
```

@@

#OG TNF
phenotype<-CD4_OG_TNF
phenotype$id<-paste(phenotype$Donor, phenotype$Stim, sep="_")
phenotype<-arrange(phenotype, id)

@@

phenotype[(phenotype$id %in% remove), numeric.only(phenotype)]<-NA
TNF<-phenotype
```

@@

>>>>

```{r read in data files}
setwd("/Applications/Old Computer/Day Lab/Flow-Data/clean")
CD4<-dplyr::select(read.csv("OG_CD4_bulk_summary_clean.csv"), -X, -X.1)
CD4_OG<-dplyr::select(read.csv("OG_CD4_OG_summary_clean.csv"), -X, -X.1)
CD4_OG_TH1<-dplyr::select(read.csv("OG_CD4_OG.TH1_summary_clean.csv"), -X, -X.1)
CD4_OG_GT<-dplyr::select(read.csv("OG_CD4_OG.TH1_summary_clean.csv"), -X, -X.1)
CD4_OG_TNF<-dplyr::select(read.csv("OG_CD4_OG.TNFa_summary_clean.csv"), -X, -X.1)
CD4_OG_IFNg<-dplyr::select(read.csv("OG_CD4_OG.IFNg_summary_clean.csv"), -X, -X.1)
PBMC<-dplyr::select(read.csv("DonorInfo_clean.csv"), -X)
    PBMC<-PBMC[grep("OG", PBMC$used),]
mimosa<-dplyr::select(read.csv("OG_MIMOSA_clean.csv"), -X)
    mimosa<-dplyr::filter(mimosa, celltype=="CD4" & Exprate==0.01)
```

@@

#OG IFNg
phenotype<-CD4_OG_IFNg
phenotype$id<-paste(phenotype$Donor, phenotype$Stim, sep="_")
phenotype<-arrange(phenotype, id)

@@

phenotype[(phenotype$id %in% remove), numeric.only(phenotype)]<-NA
TNF<-phenotype

phenotype<-CD4_OG_TNF
phenotype$id<-paste(phenotype$Donor, phenotype$Stim, sep="_")
phenotype<-arrange(phenotype, id)

phenotype[(phenotype$id %in% remove), numeric.only(phenotype)]<-NA
IFNg<-phenotype
```

@@

##PEP
```{r PEP IFNg}
library(dplyr)
library(knitr)
DF<-subset(IFNg, IFNg$Stim=="PEP")
#split by both TB and SM so you have a list of 6 data frames- each of which is a group of interest
x<-split(DF, list(DF$TB, DF$SM))
#for each dataframe in the list, return the column names of the columns where the sum of the number of rows that do not have missing data is more than 0. It's a weird double negative. But basically makes a list of the columns that have sufficient data.
y<-lapply(x, function(g) names(g[, colSums(!is.na(g)) > 0]))
#each entry in the list has to be extracted and named
a<-unlist(y[1])
b<-unlist(y[2])
c<-unlist(y[3])
d<-unlist(y[4])
#then find the intersection of all the lists. Aka which column names have sufficient data in all 4 TB-SM groups
test<-Reduce(intersect, list(a,b,c,d))
#this will also include metadata so we remove those column names and can phenotype using the standard pvals function from the beginning
colnames<-c(test[1:31], test[38:49])
for(col in colnames){
    y<-pvals_4_loose(DF, col)
    if(dim(y)[1]>0){
        print(col)
        print(y)}
}
```

### 2019-07-29 OG_cleaning.Rmd
added in a IFNg subset

write.csv(OG_CD4_bulk_summary.csv, "OG_CD4_bulk_summary_clean.csv")
write.csv(OG_CD4_OG_summary.csv, "OG_CD4_OG_summary_clean.csv")
write.csv(OG_CD4_OG.GT_summary.csv, "OG_CD4_OG.GT_summary_clean.csv")
write.csv(OG_CD4_OG.IL4_summary.csv, "OG_CD4_OG.IL4_summary_clean.csv")
write.csv(OG_CD4_OG.TH1_summary.csv, "OG_CD4_OG.TH1_summary_clean.csv")
write.csv(OG_CD4_OG.TNFa_summary.csv, "OG_CD4_OG.TNFa_summary_clean.csv")

>>>>

write.csv(OG_CD4_bulk_summary.csv, "OG_CD4_bulk_summary_clean.csv")
write.csv(OG_CD4_OG_summary.csv, "OG_CD4_OG_summary_clean.csv")
write.csv(OG_CD4_OG.GT_summary.csv, "OG_CD4_OG.GT_summary_clean.csv")
write.csv(OG_CD4_OG.IL4_summary.csv, "OG_CD4_OG.IL4_summary_clean.csv")
write.csv(OG_CD4_OG.TH1_summary.csv, "OG_CD4_OG.TH1_summary_clean.csv")
write.csv(OG_CD4_OG.TNFa_summary.csv, "OG_CD4_OG.TNFa_summary_clean.csv")
write.csv(OG_CD4_OG.IFNg_summary.csv, "OG_CD4_OG.IFNg_summary_clean.csv")
